### 2017-11-19 Authors/Algorithm-HHL/Algorithm.tex
Logical commands for different document classes

\documentclass[aps,pra,twocolumn,superscriptaddress]{revtex4-1}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{amsmath}
\usepackage{indentfirst}
\usepackage{float}
\usepackage[colorlinks]{hyperref}
\bibliographystyle{apsrev4-1}

@@

@@

Consider an unsorted database with $N$ items, Grover's algorithm require $n=\log_2^N$ qubits to represent the database, the steps of the algorithm are given as follows:

1. Initialize the qubits to $|0{\rangle ^{ \otimes n}}$, and then apply the Hadamard transform ${H^{ \otimes n}}$ on these qubits to obtain the uniform superposition state

\[|\varphi \rangle  = {H^{ \otimes n}}|0{\rangle ^{ \otimes n}} = \frac{1}{{\sqrt {{2^n}} }}\sum\limits_{x = 0}^{{2^n} - 1} {|x\rangle } \]

One can write the state $|\varphi \rangle$ to be,

\[|\varphi \rangle  = \frac{1}{{\sqrt {{2^n}} }}\sum\limits_{x = 0}^{{2^n} - 1} {|x\rangle }  = \sqrt {\frac{M}{N}} |T\rangle  + \sqrt {\frac{{N - M}}{N}} |{T_ \bot }\rangle \]
where $|T\rangle$ is the uniform superposition of $M$ target elements, and $|{T_ \bot }\rangle$ is the uniform superposition of $N-M$ non-target elements.

2. Apply the Grover iteration for about $\frac{\pi }{4}\sqrt \frac{N}{M}$ times. The iteration is described as below.

i. Apply the operator ${U_T} = I - 2|T\rangle \langle T|$.

ii. Apply the operator ${U_\varphi } = 2|\varphi \rangle \langle \varphi | - I$.

3. Measure these $n$ qubits to obtain the target elements.

>>>>

\def\pubmode{1}

\if 1\pubmode
	\documentclass[aps,pra,singlecolumn,superscriptaddress]{revtex4-1}
\fi

\if 2\pubmode
	\documentclass[aps,pra,twocolumn,superscriptaddress]{revtex4-1}
\fi

%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{amsmath}
\usepackage{indentfirst}
\usepackage{float}
\usepackage[colorlinks]{hyperref}
\bibliographystyle{apsrev4-1}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}

@@

The problem of finding specific entries in unstructured data spaces is a ubiquitous one. This class of \textit{search algorithms} have amongst the broadest applicability of any class of algorithms. Computer scientists have invested excruciating man-hours\index{SJW} into organising and structuring data so as to minimise the resource overhead (in time or space) associated with extracting desired components. However, the methodology for achieving this, and the favourability of associated resource overheads, is highly dependent on the structure of the underlying data, or whether there even is any. To this end, numerous data structures and algorithms have been developed, accommodating for every mutation and variation of the problem imaginable. Often, there is a tradeoff between the overheads induced in time and memory.

For example, \textit{hash tables}\index{Hash tables} enable theoretical $O(1)$ lookup times on data with a \textit{key-value pair}\index{Key-value pair} data structure. In a key-value pair each data entry (value) is tagged with a unique identifier (key) used for lookup. For example, when storing telephone numbers one might represent entries as key-value pairs, where the keys are people's names, and the values their respective telephone numbers. An efficient algorithm for mapping keys to physical memory addresses would imply efficient lookup of telephone numbers by name.

In the absence of a key-value representation one might simply store data in sorted form. However, this requires pre-sorting the entire data space, which may become costly for large data sets, and requires continual rearrangement whenever the data space is modified, making it computationally costly for mutable data.

For the end user, who wishes to find data elements, the worst-case data space is one with no order or underlying structure. In this instance, it can easily be seen that the best one can hope for, in terms of algorithmic runtime, is to simply look through the data space brute-force\index{Brute-force} until we find what we are looking for. For example, using the earlier analogy of the telephone book, if you were to try and use my phone number to find my name, the best you could do is start at page one and keep going until you found my name. It is clear that with an unstructured space of $N$ elements, this brute-force search algorithm requires on average $O(N)$ queries to find the desired entry. We call this the \textit{unstructured search problem}.

The brute-force classical algorithm, despite already being technically `efficient' (i.e $O(N)$ runtime), could nonetheless become unwieldy for very large datasets. The quantum search algorithm presents as solution to this problem using only $O(\sqrt{N})$ runtime, a quadratic enhancement. Whilst this falls far short of the exponential quantum enhancement one might have hoped for, it is nonetheless still extremely helpful for many purposes, given broad applications for solving this problem.

We will formulate the quantum search algorithm as an oracular algorithm, where the oracle takes as input an $n$-bit string, and outputs 1 if the input matches the entry we are looking for, otherwise 0. This formulation of the problem makes the algorithm naturally suited to solving satisfiability problems (many of which are \textbf{NP}-complete).

%%%%

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function Grover(f,n):
\begin{enumerate}
    \item Using a Hadamard transform, prepare the equal $n$-qubit superposition of all $2^n$ logical basis states,
    \begin{align}
    \ket\psi_0 &= \hat{H}^{\otimes n}\ket{0}^{\otimes n}	 \nonumber \\
    &= \frac{1}{\sqrt{2^n}}\sum_{x = 0}^{2^n - 1}\ket{x}.
    \end{align}
    \item This can be equivalently re-expressed as,
    \begin{align}
    \ket\psi_0 &= \sqrt{\frac{M}{N}}\ket{T} + \sqrt{\frac{N-M}{N}}\ket{T_\bot},
    \end{align}
  	where $\ket{T}$ is the uniform superposition of the $M$ target elements, and $\ket{T_\bot}$ the uniform superposition of the remaining \mbox{$N-M$} non-target elements.
  	\item Apply the ???? operator,
  	\begin{align}
  		\hat{U}_T = \hat{I} - 2\ket{T}\bra{T}.	
  	\end{align}
	\item Apply the ????? operator,
	\begin{align}
		\hat{U}_\varphi = 2\ket\varphi\bra\varphi - \hat{I}.
	\end{align}
	\item Measure the $n$ qubits to obtain a sample from the target elements.
	\item ???$BOX$
\end{enumerate}
}}}
\caption{.} \label{alg:quant_search}
\end{table}

### 2017-11-19 Sections/physical_architectures_for_quantum_computing.tex
Added a few stubs and comments
Logical commands for different document classes

We are then interested in the `rate'\index{Cluster state preparation rate}, $r$, at which large clusters are output from the protocol. This is simply extracted by defining a single parameter which counts the number of clusters in $\vec{n}$ above some predetermined target length, and normalises it by the total time taken to reach that point. The rate parameter converges asymptotically for long runtimes. Formally, the rate of preparation is given by,
\begin{align}
r = \lim_{t\to\infty} \frac{N_t}{t},
\end{align}
where $N_t$ is the total number of clusters of length greater than the target length at time $t$. The preparation rate is bounded by \mbox{$0\leq r\leq1$}.

@@

@@

>>>>

We are then interested in the \textit{rate}\index{Cluster state preparation rate}, $r$, at which large clusters are output from the protocol. This is simply extracted by defining a single parameter which counts the number of clusters in $\vec{n}$ above some predetermined target length, and normalises it by the total time taken to reach that point. The rate parameter converges asymptotically for long runtimes. Formally, the rate of preparation is given by,
\begin{align}
r = \lim_{t\to\infty} \frac{N_t}{t},
\end{align}
where $N_t$ is the total number of clusters of length greater than the target length at time $t$. The preparation rate is bounded by \mbox{$0\leq r\leq1$}. If the rate $r$ converges to a positive, finite value in the limit of large $t$, this implies state preparation proceeds in linear time and is therefore efficient.

@@

\ref{sec:cs_error_tele}

$n$ bonding attempts, $O(n)$ redundant qubits to measure out

@@

$n$ bonding attempts, $O(\text{log}(n))$ redundant qubits to measured out.

### 2017-11-19 Sections/quantum_algorithms.tex
Logical commands for different document classes

The algorithm implementing the Deutsch-Jozsa protocol and its circuit diagram are shown in Alg.~\ref{alg:deutsch_jozsa}. The engine room of the algorithm is in the Hadamard transform\index{Hadamard transform}, which prepares an equal superposition of all $2^n$ possible input bit-strings $x$, which are then evaluated in superposition by the oracle. To ensure unitarity, the oracle is defined to implement the transformation,
\begin{align}
	    \hat{U}_f \ket{x}\ket{y} &= \ket{x}\ket{y\oplus f(x)}.
\end{align}
That is, it flips bit $y$ if \mbox{$f(x)=1$}, equivalently addition modulo 2 or an XOR operation. An inverse Hadamard transform subsequently yields a measurement outcome with one of two possibilities:
\begin{itemize}
	\item The 0 and 1 terms outputted from the oracle interfere perfectly constructively, if the function was uniform.
	\item They interfere perfectly destructively, if the function was balanced.
\end{itemize}
Then, with a single-shot measurement of the inverse Hadamard transformed output from the oracle we establish whether $f(x)$ was balanced or uniform with certainty. This exhibits an exponential worst case speedup compared to a randomised classical sampling algorithm (which is classically optimal).

@@

\subsection{Quantum simulation} \index{Quantum simulation}\index{Hamiltonian simulation}\label{sec:quantum_sim_alg}

@@

@@

\subsection{Integer factorisation} \index{Shor's algorithm}

@@

@@

>>>>

The algorithm implementing the Deutsch-Jozsa protocol and its circuit diagram are shown in Alg.~\ref{alg:deutsch_jozsa}. The engine room of the algorithm is in the Hadamard transform\index{Hadamard transform}, $\hat{H}^{\otimes n}$, which prepares an equal superposition of all $2^n$ possible input bit-strings $x$, which are then evaluated in superposition by the oracle. To ensure unitarity, the oracle is defined to implement the transformation,
\begin{align}
	    \hat{U}_f \ket{x}\ket{y} &= \ket{x}\ket{y\oplus f(x)}.
\end{align}
That is, it flips bit $y$ if \mbox{$f(x)=1$}, equivalently addition modulo 2 or an XOR operation. An inverse Hadamard transform subsequently yields a measurement outcome with one of two possibilities:
\begin{itemize}
	\item The 0 and 1 terms outputted from the oracle interfere perfectly constructively, if the function was uniform.
	\item They interfere perfectly destructively, if the function was balanced.
\end{itemize}
Then, with a single-shot measurement of the inverse Hadamard transformed output from the oracle we establish whether $f(x)$ was balanced or uniform with certainty. This exhibits an exponential worst case speedup compared to a randomised classical sampling algorithm (which is classically optimal).

@@

\subsection{Quantum simulation} \index{Quantum chemistry}\index{Quantum simulation}\index{Hamiltonian simulation}\label{sec:quantum_sim_alg}

@@

\comment{Discuss quantum chemistry as leading application}

@@

\subsection{Integer factorisation} \index{Shor's algorithm}\index{Hidden subgroup problem}\index{Period-finding algorithm}\index{Discrete logarithm algorithm}

@@

\comment{Mention relationship to hidden subgroup, period-finding, and discrete-log problems}

While this algorithm is known to reside in \textbf{BQP}, it is strongly believed not to be \textbf{BQP}-complete. Similarly, while it is known to reside in \textbf{NP}, it is strongly believed not to be \textbf{NP}-complete, thereby placing it in the `limbo zone' of \textbf{NP}-intermediate complexity.\index{\textbf{NP}-intermediate}

@@

%
% Intermediate Models for Quantum Computation
%

\subsection{Intermediate models for quantum computation}

\comment{To do}

\comment{Boson-sampling and IQP. Other sampling problems.}
